Performance of Magnetic Refrigerators Operating with Different Magnetic Profiles

### 2019-09-09 PaperMagneticProfiles_JBSMSE.tex
Develop better draft of Introduction.

\usepackage{graphicx}
\usepackage{subfig}

@@

An active magnetic regenerator (AMR)  is a thermal regenerator composed of a solid porous matrix of magnetocaloric material, which changes its temperature according to the application of a varying magnetic field in synchronization with oscillatory fluid flows, due to the so-called magnetocaloric effect (MCE). Active magnetic regenerators are employed in magnetic refrigeration, a promising alternative to vapor compression systems due to its use of non-gaseous refrigerants and potentially higher  thermodynamic efficiency \cite{bib:trevizoli}. A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}. Since the working fluid only has energy transport functions and does not change its phase, aqueous solutions with freezing and corrosion inhibitors are usually employed.

The dynamic nature of AMR systems are described by two characteristic waveforms:

\begin{enumerate}
\item The \emph{magnetic profile}, which describes the time variation of the magnetic field experienced by the regenerators;
\item The \emph{fluid flow profile}, which describes the oscillatory flow rate though the regenerators
\end{enumerate}

Different combinations and arrangements of these waveforms yield different thermodynamic cycles through which an AMR system can operate. The most common cycle in the literature is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}. During magnetization, the solid material warms up due to the MCE; with a constant applied magnetic field, fluid flows, absorbing this energy and releasing it in the hot heat exchanger; the magnetic field is changed to a low level, cooling down the material; fluid from the hot source flows through the bed, releases its energy to the material, and the cold fluid can then absorb heat from the cold source.

\begin{figure}[!ht]
  \centering
 %\includegraphics[width=5cm]{brayton-kitanovski}
  \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
  \label{fig:brayton}
\end{figure}

The performance of AMR-based magnetic refrigerators is directly related to their thermodynamic cycle, and hence to the magnetic and fluid flow profiles. With this motivation, there are multiple studies in the literature regarding these waveforms. In general, the fluid flow profile is more easily changed in experimental prototypes with modifications in the hydraulic system, and it can be optimized for a given magnetic profile for higher cooling capacity or coefficient of performance \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}. The actual shape of waveform depends on the hydraulic system configuration; single- or two-regenerators systems usually employ piston pumps with sinusoidal fluid flow profiles, while more complex valving system yield trapezoidal fluid flow profiles, with periods of no flow (when fluid is by-passed from the regenerator), periods with a constant flow rate and ramp transitions between these two states.

In room temperature magnetic refrigeration, the magnetic profile is generated by permanent magnets, representing the most expensive part of a magnetic refrigerator \cite{bib:bjoerk16_lifetime}, and hence considered fixed in AMR devices. Although the magnetic profile can be changed with motion control on the permanent magnets \cite{bib:benedict16_desig}, this is a topic yet to be better investigated, and most studies on the subject are numerical. The ideal Brayton cycle requires a instantaneous magnetic profile (square waveform), but in practice it is difficult to generate  stepwise variations of the magnetic field  using rotating permanent magnets arrays. Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.

Many works on the analysis of  magnetic profiles use a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets. The performance of an AMR subjected to a ramp magnetic profile and a instantaneous fluid flow profile with different parameters has been investigate \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles. A study that  implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations) \cite{bib:kitanovski} concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance. The conclusion that the instantaneous magnetic profile results in higher cooling capacities for a given temperature span, compared to other waveforms is also presented in \cite{bib:asme-mce}

In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field (${B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles_all.eps}
  \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
  \label{fig:cycles}
\end{figure}

The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous, rectified cosine and ramp magnetic  profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application. In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate. In particular, in comparison with the work of \cite{bib:kitanovski}, where the authors studied different combinations of flow and magnetic profiles to yield various thermodynamic cycles, we fix the fluid flow profile to better investigate the effect of the magnetic profile, which is used in the design of magnetic circuits.

>>>>

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage{nomencl}
\usepackage{hyperref}

@@

Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint. The large entropy generation associated with vapor compression processes makes this techonology constrained by low exergy efficiencies, in particular for compact systems \cite{KITANOVSKI2015288}. In addition, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technologial challenges \cite{bib:lionte18-adapt}.

The term \emph{caloric cooling} is \textcolor{black}{generally} applied to alternative cooling techonologies in which the cooling effect is generated by the response of a solid material to a physical \textcolor{black}{stimulus}. The absence of hazardous gases, compressors \textcolor{black}{and throttling devices} makes these technologies potentially more efficient, \textcolor{black}{scalable}, silent and environmentally friendly. Magnetic refrigeration (MR) is the most advanced of all caloric technologies \cite{KITANOVSKI2015288}; in particular, with the classes of magnetic refrigerants currently available, magnetocaloric refrigeration seems promising for applications in small temperature span (around \SI{20}{\kelvin}), such as winecoolers \textcolor{black}{and air conditioners} \cite{KITANOVSKI2015288}.

\nomenclature[vm]{MR}{Magnetic (or Magnetocaloric) Refrigeration}

In magnetic refrigeration, a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE). The magnitude of the MCE  \textcolor{black}{depends} on  parameters \textcolor{black}{related to} characteristics of the material, magnetic field variation and temperature, and its maximal at the transition Curie temperature of the material. For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.

\nomenclature[vm]{MCM}{Magnetocaloric Material}

For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}. \textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and is cyclically magnetized and demagnetized to activate the magnetocaloric effect.  \textcolor{black}{A regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}. These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.

\nomenclature[vm]{AMR}{Active Magnetic Regenerator}

The five main subsystems in an AMR-based magnetic refrigerator can be identified as follows \cite{bib:jaime,bib:trevizoli16_pump}:

\begin{enumerate}
\item magnetic circuit; \label{item:1}
\item active magnetic regenerator; \label{item:2}
\item flow management system; \label{item:3}
\item control system; \label{item:4}
\item transmission system; \label{item:5}
\item heat exchangers and cabinet. \label{item:6a}
\end{enumerate}

The magnetic circuit generates oscillating magnetic fields that activate the MCE \textcolor{black}{in} the active magnetic regenerators. As previously explained, the regenerators are composed of magnetocaloric porous media, and the flow management system provides the alternating fluid flow through the beds. The control system \textcolor{black}{serves} the purpose of synchronizing the fluid flow regime with the magnetic field variations. Finally, the heat exchangers are responsible for transferring the cooling effect from the AMR to the refrigerated cabinet and the rejected heat to the surroundings.

Magnetic refrigerators can operate according to different thermodynamic cycles, but the stages are roughly as follows. The magnetic circuit magnetizes the MCM, increasing its temperature due to the MCE. During the so-called \emph{cold blow}, cold fluid from the cold source flows through the warm bed and absorbs its energy, releasing it to the external heat exchanger. On the return of the fluid, the solid is demagnetized and cooled down, and in the \emph{hot blow} the fluid relases energy to the bed, decreasing its temperature so it can absorb the thermal load at the cold source. The cycle then repeats; different cycles can be configured by different durations and synchronization steps between these two \emph{characteristic waveforms}:

\begin{enumerate}
\item The \emph{magnetic profile}, which describes the oscillating magnetic field over one regenerator;
\item The \emph{fluid flow profile}, which describes the time-variation of flow rate through one bed.
\end{enumerate}

Among the challenges cited in the literature for further improvement of magnetic refrigerators, two can be highlighted \cite{bib:eriksen16_activ}:

\begin{enumerate}
\item Better use of AMR and magnetic circuit models during the design process, to identify optimal geometric and operating parameter;
\item Better study of losses that are present in a magnetic cooling device.
\end{enumerate}

\textcolor{black}{In} other words, these challenges arise due to \emph{interactions} between different subsystems \textcolor{black}of a magnetic refrigerator. In these context, the focus on the aforementioned waveforms is a suitable approach for optimizing the performance of magnetic refrigerators, as these profiles represent interactions between systems. As it will be seen, mathematical models for AMRs take these waveforms as input, and they are generated by models for other components.

Fluid flow profiles are more easily investigated with experimental methods, since they can be altered with modifications in the fluid flow system. In particular, the \emph{duration} of blows have been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}, and the literature shows that the cooling capacity of magnetic refrigerators can be increased by focusing fluid flows during periods where the magnetic field is at its extrema values.

In this work, we focus on magnetic profiles, which are less studied in the literature. The studied waveforms are depicted in \autoref{fig:profiles}, identified by the transitions between states. The instantaneous profile represents step-like changes between high and low levels of the magnetic field, while the ramp profile has linear variations between these states. The rectified cosine profile is a common waveform found in the literature that has a continuous variation of the applied magnetic field.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{profiles_all}
  \caption{Magnetic profiles studied in this paper}
  \label{fig:profiles}
\end{figure}

The instantaneous magnetic profile is characteristic of the Brayton AMR cycle, where the magnetization and demagnetization steps must be done adiabatically, as shown in \autoref{fig:brayton}; compared to other common cycles such as the Ericsson, the Brayton cycle results in the highest cooling capacities for the same operating  parameters \cite{bib:kitanovski}, at the expense of lower coefficient of performance.

\begin{figure}[!ht]
  \centering

  \caption{Brayton AMR cycle}
  \label{fig:brayton}
\end{figure}

 In practice, the ramp profile is a more feasible realization with finite transition times, and its synchronization with the fluid flow profile can yield different performance levels \cite{TUSEK20111507}. In particular, the plateaus of magnetic field should be centered with the blow durations \cite{bib:bjoerk11_amr}.
\autoref{fig:sync} shows the syncronization schema between the magnetic and fluid flow profiles, showing the ramp magnetic profile as an example.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{profiles_rm_and_flow_instantaneous}
  \caption{Ramp magnetic profile (solid lines) and instantaneous fluid flow profile (dashed lines)}
  \label{fig:sync}
\end{figure}

This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}. However, their amplitudes was not varied, nor were they investigated with different geometries.

The present works combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms. These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile. The fluid flow profile is assumed fixed in shape, although its parameters are also variied. The emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
